\\fontsize{12pt}{3pt}\\selectfont \\textbf{\\textit{Journal: Ecosphere. Manuscript ID: ECS23-0342. Manuscript type: Article}}

### 2024-02-12 manuscript/manuscriptRW.Rmd
comment8: letteri is too small, revise the gfigure

First, some models overestimated recruitment across the entire gradients of at least one of the five main tree species (Figure 8, e.g., ForCEEPS, ForCEEPS(f), LandClim or LPJ-GUESS), while other models overestimated recruitment of more than one species for a large part of the climate gradients, such as xComp, PICUS, SIBYLA or LPJ-GUESS (cf. red colors in Figure 8). These trends were consistent for both recruitment thresholds, although the exact changes in the share of the recruited basal area were different (Appendix S1: Figure S8).

@@

Lastly, there is no model that performed well across the five species regarding the species-specific recruitment levels in the environmental space (Figure 8). Some models (e.g., ForClim11, PICUS) tended to consistently overestimate the recruitment share of all five species, but most models overestimated the recruitment share of some species while underestimating the share of others (e.g., ForCEEPS, LPJ-GUESS).

>>>>

First, some models overestimated recruitment across the entire gradients of at least one of the five main tree species (Figure 10, e.g., ForCEEPS, ForCEEPS(f), LandClim or LPJ-GUESS), while other models overestimated recruitment of more than one species for a large part of the climate gradients, such as xComp, PICUS, SIBYLA or LPJ-GUESS (cf. red colors in Figure 10). These trends were consistent for both recruitment thresholds, although the exact changes in the share of the recruited basal area were different (Appendix S1: Figure S8).

@@

Lastly, there is no model that performed well across the five species regarding the species-specific recruitment levels in the environmental space (Figure 10). Some models (e.g., ForClim11, PICUS) tended to consistently overestimate the recruitment share of all five species, but most models overestimated the recruitment share of some species while underestimating the share of others (e.g., ForCEEPS, LPJ-GUESS).
